---
title: "untrader"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{untrader}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Installation

Install the package from the github repository. 

```{r installation,eval=F}
devtools::install_github('datapumpernickel/untrader')
```

# Authentication

To query data from the Comtrade API, you will need to make an account at [https://comtradeplus.un.org/](https://comtradeplus.un.org/). Once you made your account, you need set up a primary and secondary key in your profile at the UN website. See their [wiki](https://unstats.un.org/wiki/display/comtrade/New+Comtrade+User+Guide) for details (Scroll until you reach `UN Comtrade API Management`).  

Once you have your API key, you need to make the API key available to `untrader`. For this, you can either set your key through the interactive function and save it for the current session, or set it permanently in your environment. 

### Set it in current session

When prompted, put the API key in.

```{r set primary key,eval=F}
untrader::set_primary_comtrade_key()
```

You can test that the API key is correctly stored, by trying to call the following function. Beware not to evaluate the following function in a markdown document you intend on sharing, as you might leak your API key. 

```{r get key,eval=F}
untrader::get_primary_comtrade_key()
```


### Permanently setting your API key

You can also permanently set your API key either for the current project or your whole user environment. For this you need to edit your .Renviron file (see [here](https://rstats.wtf/r-startup.html#renviron) for more info on environment file and variables).

You can use `usethis::edit_r_environ()` to edit your .Renviron file. The variable name that `get_comtrade_data()` will be looking for is: `COMTRADE_PRIMARY` and you need to name it accordingly. 

If for some reason, you want to set the API key manually, you can also pass it on to the `get_comtrade_data()` function with the parameter `primary_key`. 

# Getting data from Comtrade

When getting data from comtrade, you will need to set values for most parameters, as there is no sensitive default for some of them. 

```{r error with no params,eval=F}
untrader::get_comtrade_data()
```

If you are for example interested in the exports of "Beer made from malt", HS code [2203](https://www.tariffnumber.com/2023/2203) from Germany to Austria, in the year 2010, you would use the following code. 

```{r valid request,eval=F}
untrader::get_comtrade_data(frequency =  'A',
                   commodity_classification = 'HS',
                   commodity_code = '2203',
                   flow_direction = 'export',
                   reporter = "DEU",
                   partner = 'AUT',
                   start_date = 2010,
                   end_date = 2010,
                   verbose = T,
                  process = T)
```
